EE454 Project 1 Report

### 2015-09-24 p1/report/latex/draft.tex
Fixed Comma
polish

@@

\newpage
\includepdf[pages={1}]{../FlowChart_pdf_1b.pdf}

@@

@@

Observation of the output from each layer is consistent with the project description.  Normalization produces an image with scaled pixel values but is relatively unchanged.  Convolution produces a set of images with different feature sets extracted.  The ReLu produces an image with a 0 threshold (MATLAB's imagesc command slightly changes the output image because the range of the pixel values in the image changes).  Max Pooling reduces the size of the image by a factor of (nxn) and has the effect of making the previous image look more ``blocky'' via down-sampling.  Finally, we have the fully-connected layer and the soft max layer which produce a vector of classification probabilities from the image which are represented by the bar graph.

@@

\section{Member Contributions}
	Overall the contributions made form each team member were pretty even. Whenever the team met to work on the project most of the team members were in attendance. Everyone who was in attendance at each team meeting attempted to work on a different piece of the project to ensure that we were making steady progress. The coding was not split up evenly as one team member did not attend the initial meeting and as a result he missed most of the actual coding and basically all of the design decisions. We attempted to split the report up evenly, but as the deadline approached scheduling meetings became difficult and some individuals were unavailable to work on the report. In conclusion, the work was not split up evenly among our four group members, but everyone attempted to contribute.

>>>>

Given a set of images where each image falls into a class, the neural net should be able to take the image as input and label the image.  The test images provided also have ground-truth classifications; so, we can compare the results of the CNN with the ground truth labels to obtain a measure of accuracy.

@@

@@

\includepdf[pages={1}]{../FlowChart_pdf_1b.pdf}

@@

\subsection{Visual Verification}

Observation of the output from each layer is consistent with the project description.  Normalization produces an image with scaled pixel values, but is relatively unchanged.  Convolution produces a set of images with different feature sets extracted.  The ReLu produces an image with a 0 threshold (MATLAB's imagesc command slightly changes the output image because the range of the pixel values in the image changes).  Max Pooling reduces the size of the image by a factor of (nxn) and has the effect of making the previous image look more ``blocky'' via down-sampling.  Finally, we have the fully-connected layer and the soft max layer which produce a vector of classification probabilities from the image which are represented by the bar graph.

\subsection{Analytical Verification}
Passing the test image provided through our Neural Net produces the following probability vector:\\~\\
\begin{tabular}{| c | c | c | c | c | c | c | c | c | c |}
\hline
0.525 & 0.004 & 0.067 & 0.120 & 0.018 & 0.019 & 0.014 & 0.009 &	0.210 & 0.010 \\
\hline
\end{tabular}

~\\ This probability vector is the same as the probability vector provided in the test data (and indicates a correct classification of airplane).  While not rigorous proof, this result is indicative of correctness.  Additionally, at every layer of the CNN, we verified that the test layer output provided was the same as the output produced by our Neural Net.

@@

\section{Member Contributions}
	Overall the contributions made from each team member were pretty even. Whenever the team met to work on the project most of the team members were in attendance. Everyone who was in attendance at each team meeting attempted to work on a different piece of the project to ensure that we were making steady progress. The coding was not split up completely evenly: much of the coding work was tasked by layer, and each layer did not constitute the same amount of work.  We attempted to split the report up evenly, but as the deadline approached scheduling meetings became difficult and some individuals were unavailable to work on the report. In conclusion, the work was not split up evenly among our four group members, but everyone attempted to contribute.
